% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2018 Jason R. Blevins <jblevins@xbeta.org>
% https://jblevins.org/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

% Modified by Srisharan Shreedharan on December 20, 2018.

\documentclass[11pt,letterpaper]{article}

% Set your name here
\def\name{Srisharan Shreedharan}

% Load packages
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem} % Enumerate with [resume] option
\usepackage{etaremune} % Enumerate in reverse order for pubs
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {friction, faulting, rock mechanics,earthquakes},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
      \setlength{\leftmargin}{1.5em}
      \setlength{\itemsep}{0.25em}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0.25em}
    }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}


\begin{document}

% Place name at left and date at right
\MakeUppercase{\huge\name}

% Alternatively, print name centered and bold:
%\centerline{\titlefont{\name}}

% Contact Information
\bigskip
\begin{minipage}[t]{0.495\textwidth}
  Department of Geosciences \\
  The Pennsylvania State University \\
  439 Deike \\
  University Park, PA 16802 
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  \href{https://srisharan.github.io/}{srisharan.github.io} \\
  \href{mailto:srisharan@psu.edu}{srisharan@psu.edu} \\
  (520) 286-7831
\end{minipage}

%%%%%%% EDUCATION %%%%%%%%

\section*{Education}
\begin{itemize}
  \item Ph.D., Geosciences, The Pennsylvania State University, {\bf 2021 (expected)}.

  \item M.S., Geological Engineering, The University of Arizona, {\bf 2016}.

  \item B.Tech., Mining Engineering, National Institute of Technology, Karnataka, {\bf 2014}.
\end{itemize}


%%%%%%% EMPLOYMENT %%%%%%%%


\section*{Employment}
\begin{itemize}

    \item Research  Assistant, Chris Marone/Demian Saffer, Penn State Rock and Sediment Mechanics Lab, {\bf 2016 -- Present}.
      
    \item Research Assistant, Pinnaduwa Kulatilake, Rock Mass Modeling and Computational Rock Mechanics Laboratories, The University of Arizona, {\bf 2014 -- 2016}.
    
    \item Undergrad Research Intern, Department of Civil Engineering, Indian Institute of Technology (IIT) - Madras, India, {\bf Summer 2013}.
    
    \item Undergrad Research Intern, Julius Kruttschnitt Mineral Research Centre (JKMRC), The University of Queensland, Australia, {\bf Winter 2012}.
\end{itemize}


%%%%%%% AWARDS %%%%%%%%


\section*{Honors \& Awards}
\begin{itemize}
    \item US Science Support Program (USSSP) Post Expedition Award, IODP Expedition 375, {\bf Fall 2018} 
    \item AGU Outstanding Student Paper Award, Seismology section, {\bf Fall 2017}
    \item Shell Geosciences Energy Research Facilitation Award, {\bf 2017, 2018} 
    \item Paul D. Krynine Travel Award, {\bf 2017, 2018}
    \item Arnulf I. Muan Graduate Fellowship in Earth and Mineral Sciences, {\bf 2016 -- 17}
    \item Penn State University Graduate Fellowship, {\bf 2016 -- 17}
    \item Society for Mining, Metallurgy and Exploration Tucson Scholarship, {\bf 2015 -- 16}
    \item The Women's Auxiliary to the American Institute of Mining, Metallurgical and Petroleum Engineers Scholarship, {\bf 2015 -- 16} 
    \item The University of Arizona Graduate Tuition Scholarship, {\bf 2014 -- 16} 
    \item Neyveli Lignite Corporation (NLC) Gold Medal for best outgoing student in NITK, {\bf 2014}
    \item The University of Queensland Summer Research Scholarship, {\bf 2012} 
\end{itemize}


%%%%%%% PUBLICATIONS %%%%%%%%


\section*{Peer-Reviewed Publications}
\begin{etaremune}
    \item Saffer, D. M., Wallace, L. M., Petronotis, K., and the {\bf Expedition 375 Scientists}. (2018). {\em Expedition 375 Preliminary Report: Hikurangi Subduction Margin Coring and Observatories.} International Ocean Discovery Program. \href{https://doi.org/10.14379/iodp.pr.375.2018}{doi: 10.14379/iodp.pr.375.2018}
    \item Huang, G., Kulatilake, P. H. S. W., {\bf Shreedharan, S}., Cai, S., Song, H. (2017). 3-D Discontinuum Numerical Modeling of Subsidence incorporating Ore Extraction and Backfilling Operations in an Underground Iron Mine in China. {\em International Journal of Mining Science and Technology, 27}(2), 191-201. \href{http://www.sciencedirect.com/science/article/pii/S2095268617300617}{doi: 10.1016/j.ijmst.2017.01.015}
    \item Ram Chandar, K., Sastry, V. R., Hegde, C., {\bf Shreedharan, S}. (2016). Prediction of Peak Particle Velocity using Multi Regression Analysis. {\em Geomechanics and Geoengineering. }\href{http://www.tandfonline.com/doi/abs/10.1080/17486025.2016.1184763}{doi: 10.1080/17486025.2016.1184763} 
    \item Kulatilake, P. H. S. W., {\bf Shreedharan, S.}, Sherizadeh, T., Shu, B., He, P., Xing, Y. (2016). Laboratory Estimation of Rock Joint Stiffness and Frictional Parameters. {\em Geotechnical and Geological Engineering,34 }(6), 1723-1735. \href{http://link.springer.com/article/10.1007/s10706-016-9984-y}{doi: 10.1007/s10706-016-9984-y}
    \item {\bf Shreedharan, S.}, Kulatilake, P. H. S. W. (2015). Discontinuum-Equivalent Continuum Analysis of the Stability of Tunnels in a Deep Coal Mine using the Distinct Element Method. {\em Rock Mechanics and Rock Engineering, 49}(5), 1903-1922. \href{http://link.springer.com/article/10.1007/s00603-015-0885-9}{doi: 10.1007/s00603-015-0885-9}
    \item {\bf Shreedharan, S.}, Hegde, C., Sharma, S., Vardhan, H. (2014). Acoustic Fingerprinting for Rock Identification during Drilling. {\em International Journal of Mining and Mineral Engineering, 5}(2), 89-105. \href{http://www.inderscienceonline.com/doi/abs/10.1504/IJMME.2014.060193}{doi: 10.1504/IJMME.2014.060193}
\end{etaremune}


%%%%%%% PUBS IN PROGRESS %%%%%%%%


\section*{In Prep}
\begin{etaremune}
    \item {\bf Shreedharan, S.}, Rivi\`ere, J., Bhattacharya, P., Marone, C. Frictional State Evolution during Normal Stress Perturbations Probed with Ultrasonic Waves. {\em JGR: Solid Earth (In review)}
\end{etaremune}


%%%%%%% CONFERENCES %%%%%%%%


\section*{Conference Abstracts \& Presentations}
\textsuperscript{$\dagger$} -- Presenting Author
\begin{etaremune}
    \item {\bf Shreedharan, S.}\textsuperscript{$\dagger$}, Rivi\`ere, J., Ryan, K., Marone, C. (2018). Precursory changes in p- and s- phase amplitudes and velocities linked to accelerated fault creep during laboratory slip instabilities. {\em AGU Fall Meeting 2018, Washington DC}. (Invited Talk)
    \item {\bf Shreedharan, S.}\textsuperscript{$\dagger$}, Rivi\`ere, J., Marone, C. (2018). Probing changes in frictional state due to normal stress perturbations using controlled-source ultrasonics. {\em AGU Fall Meeting 2018, Washington DC}. (Poster)
    \item Rabinowitz, H.S.\textsuperscript{$\dagger$}, Savage, H.M., {\bf Shreedharan, S.}, Ikari, M., Meneghini, F., Ito, Y., Kitajima, H., Wallace, L.M., Saffer, D.M., Petronotis, K., and the Expeditions 372/375 Scientists. (2018). Frictional behavior of incoming sediment in the Hikurangi subduction zone at {\em in-situ} PT conditions. {\em AGU Fall Meeting 2018, Washington DC}. (Poster)
    \item Savage, H.M.\textsuperscript{$\dagger$}, Coffey, G.L., {\bf Shreedharan, S.}, Polissar, P.J., Fagereng, A., Meneghini, F., Morgan, J., Wang, M., Hashimoto, Y., Wallace, L.M., Saffer, D.M., Barnes, P., Pecher, I.A., Petronotis, K., LeVay, L., and the Expeditions 372/375 Scientists. (2018). Signatures of Brittle Deformation in a Shallow Fault in the Hikurangi Subduction Margin. {\em AGU Fall Meeting 2018, Washington DC}. (Poster)
    \item Jeppson, T.\textsuperscript{$\dagger$}, Kitajima, H., Ikari, M., Lee, H., Ito, Y., Harris, R., {\bf Shreedharan, S.}, ..., Wallace, L.M., Saffer, D.M., Parnes, P., Pecher, I.A., Petronotis, K., LeVay, L., and the Expeditions 372/375 Scientists. (2018). Lithology and cement controls on the evolution of compressional wave velocity and porosity in input materials at northern Hikurangi and other subduction zones. {\em AGU Fall Meeting 2018, Washington DC}. (Poster)
    \item Ryan, K.\textsuperscript{$\dagger$}, {\bf Shreedharan, S.} (2018). Rubbing and pressing rocks together with a big computer controlled press to learn about the times when the ground shakes a lot as pieces of the world move around. {\em AGU Fall Meeting 2018, Washington DC}. (Talk)
    \item {\bf Shreedharan, S.}\textsuperscript{$\dagger$}, Rivi\`ere, J., Bhattacharya, P., Marone, C. (2018). The Sound of Friction: Probing Fault Microphysics During Normal Stress Variations Using Controlled-Source Ultrasonics. {\em Penn State Geodynamics Seminar}. (Talk)
    \item {\bf Shreedharan, S.}\textsuperscript{$\dagger$}, Rivi\`ere, J., Marone, C. (2018). Precursory Changes in p- and s- Phase Amplitudes and Velocities Linked to Accelerated Fault Creep During Laboratory Slip Instabilities. {\em Gordon Research Conference on Rock Deformation 2018}. (Poster)
    \item {\bf Shreedharan, S.}\textsuperscript{$\dagger$}, Rivi\`ere, J., Marone, C. (2017). Frictional Response of Simulated Faults to Normal Stress Perturbations probed with Ultrasonic Waves. {\em AGU Fall Meeting 2017, New Orleans}. (Poster)
    \item {\bf Shreedharan, S.}\textsuperscript{$\dagger$}, Rivi\`ere, J., Bolton, C., Zheng, L., Johnson, P., Marone, C. Characterization of Acoustic Emissions From Laboratory Stick-Slip Events in Simulated Fault Gouge. {\em ARMA Symposium - 51th US Rock Mechanics Symposium, Houston}. (Talk)
    \item {\bf Shreedharan, S.}\textsuperscript{$\dagger$}, Rivi\`ere, J., Marone, C. (2017). Frictional Response of Simulated Faults to Normal Stress Perturbations probed with Ultrasonic Waves. {\em 49th Annual Geosciences Graduate Student Colloquium}. Pennsylvania State University. (Talk)
    \item Kulatilake, P. H. S. W.\textsuperscript{$\dagger$}, {\bf Shreedharan, S.}, Huang, G., Cai, S., Song, H. (2016). 3-D Discontinuum Numerical Modeling of Ore Extraction, Backfilling and Subsidence in an Underground Iron Mine in China. {\em ARMA Symposium - 50th US Rock Mechanics Symposium, Houston}. (Talk) 
    \item {\bf Shreedharan, S}.\textsuperscript{$\dagger$}, Kulatilake, P. H. S. W. (2016). Distinct Element Method Based Stability Analysis of Tunnels in a Deep Coal Mine in China. {\em ARMA Symposium - 50th US Rock Mechanics Symposium, Houston}. (Poster)
\end{etaremune}


%%%%%%% TECHNICAL SKILLS %%%%%%%%


\section*{Technical Skills}
\begin{itemize}
    \item {\em Programming languages}: Python, C++, R, Fish
    \item {\em General engineering tools}: MATLAB, ANSYS, COMSOL, Solidworks
    \item {\em Geologic modeling tools}: FLAC, 3DEC, PFC2D/3D, Rocscience Suite, Petrel, ProMAX
\end{itemize}


%%%%%%% TEACHING %%%%%%%%


\section*{Teaching}
\begin{itemize}
    \item GEOSC497: Multi-Channel Seismic Processing - "An Introduction to Marine Seismic Data Acquisition", {\bf Fall 2017}.
    \item GEOSC508: The Mechanics of Earthquakes and Faulting - "Building a Wheatstone's Bridge Strain Gauge Circuit - Demo", {\bf Fall 2017}.
    \item MN302: Mine Environment and Ventilation - Prepared free online lecture material available online at \href{www.nptel.ac.in}{www.nptel.ac.in}, {\bf 2012 -- 13}.
\end{itemize}


%%%%%%% FIELD EXERIENCE %%%%%%%%


\section*{Field Experience}
\begin{itemize}
    \item {\em R/V JOIDES Resolution} - IODP 375: Hikurangi Slow Earthquakes, Petrophysicist, {\bf  2018}. 
    \item {\em R/V Revelle} - Multi-Channel Seismic data acquisition cruise at Cascadia Margin, {\bf  2017}.
    \item Fracture mapping survey for slope stability analysis using LiDAR scanning and 3D photogrammetry at Singareni coal mines, {\bf  2012}.
    \item Field deployment of geophones for blast vibration monitoring survey at Singareni coal mines, {\bf  2012}.
\end{itemize}


%%%%%%% SERVICE %%%%%%%%


\section*{Service}
\begin{itemize}
    \item Reviewer for \href{https://www.journals.elsevier.com/earth-and-planetary-science-letters}{\em Earth and Planetary Science Letters}, \href{https://www.journals.elsevier.com/journal-of-computational-science/}{\em Journal of Computational Science} and \href{http://www.inderscience.com/jhome.php?jcode=ijogct}{\em International Journal of Oil, Gas and Coal Technology}
    \item Co-chair of the Department of Geoscience Computer Users' Group, {\bf 2017 -- Present}
    \item Penn State Department of Geoscience Grad Colloquium Committee, {\bf 2018 -- 19}
    \item Penn State Graduate Research Exhibition poster judge, {\bf 2017}
    \item Graduate and Professional Students' Council Travel Grants Judge, The University of Arizona, {\bf 2015 -- 2016}
\end{itemize}


%%%%%%% OUTREACH %%%%%%%%


\section*{Outreach and Miscellany}
\begin{itemize}
    \item Rock Climbing Instructor, State College YMCA, {\bf 2017 -- Present}
    \item Earth and Mineral Science Exposition Open House at Penn State - A virtual tour of the R/V JOIDES Resolution, {\bf  2018}
    \item Shake, Rattle, Rocks geology outreach for State College school district fifth graders, {\bf 2017}
\end{itemize}


%%%%%%% MEMBERSHIPS %%%%%%%%


\section*{Professional Memberships}
\begin{itemize}
    \item American Geophysical Union
    \item American Rock Mechanics Association
    \item Seismological Society of America
\end{itemize}


\end{document}

%%% Local Variables: 
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% End: 